FoRTE baseline

### 2019-10-01 analysis/paper/paper.Rmd
Fix references to minimum_height in text and table

- Fraction of litter carbon that enters the labile (fast) soil carbon pool (`f_labile`)
- Minimum plant height for reproduction (`minimum_height`)
- Soil-plant water conductance, or "water availability factor" (`water_conductance`)
- C:N ratio in fine roots (`c2n_fineroot`) and leaves (`c2n_leaf`)
- Leaf turnover rate (evergreen-only; `leaf_turnover_rate`)
- Proportion of dispersal that is "global" (`nonlocal_dispersal`) <!-- TODO What is this? Can I drop it from the analysis? -->

>>>>

- Fraction of litter carbon that enters the labile (fast) soil carbon pool (`f_labile`)
- Minimum plant height for reproduction (`repro_min_h`)
- Soil-plant water conductance, or "water availability factor" (`water_conductance`)
- C:N ratio in fine roots (`c2n_fineroot`) and leaves (`c2n_leaf`)
- Leaf turnover rate (evergreen-only; `leaf_turnover_rate`)
- Proportion of dispersal that is "global" (`nonlocal_dispersal`) <!-- TODO What is this? Can I drop it from the analysis? -->
